---
title: "README"
author: "Guangkun Bao"
date: "2020/9/12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Computing Environment
operating system : Windows 10
R : version 4.0.2
Rstudio : Version 1.2.5019

Following the instruction from [*Compile Hadley’s Advanced R to a PDF*](http://brettklamer.com/diversions/statistical/compile-hadleys-advanced-r-programming-to-a-pdf/).

In the progress, I've met several problems. The followings are the errors I've met.


## Packages missing or need to be reinstall.

The problematic packages is as follows:

rlang, glue, ellipsis, vctrs, pillar, tibble, purrr, bookdown, lobstr, dplyr, tidyverse, RSQLite, profvis, bench, ggbeeswarm.

solution: 
Use 
```{r, eval = FALSE}
install.packages()
```

## Can't knit Introduction.Rmd

Quitting from lines 223-235 (Introduction.Rmd) 

solution:
Adding `encoding = "UTF-8"` in line 224.

## Warning message not shown correctly

In [*Vectors.Rmd*] it use `as.integer(c("1", "1.5", "a"))` to illustrate failed coercion of strings can generates a warning and a missing value.

However my system language is Chinese so the warning message can not be shown correctly.

solution: 
Use 
```{r, eval = FALSE}
Sys.setenv(LANGUAGE = "en")
```

## 'make' not found

Warning message: In system(cmd) : 'make' not found

solution:
Install Rtools40(https://cran.r-project.org/bin/windows/Rtools/) and do it from R like so:
```{r, eval = FALSE}
writeLines('PATH="${RTOOLS40_HOME}\\usr\\bin;${PATH}"', con = "~/.Renviron")
```

## Fonts not found and some unknown mistake

The problem started with font "Inconsolata" cannot be found.
However, after download it from [*Google Fonts*](https://fonts.google.com/specimen/Inconsolata) and install it. The problem still exists.

Then I try Miktex instead of TinyTex. This time the problem turned into: **"xelatex" not found**. Even if I add root directory into PATH.

Finally, I try to combine Miktex and Tinytex and the problem turned into: `! xdvipdfmx:fatal: Invalid TTC index (not TTC font): C:/WINDOWS/fonts/Inconsolata-VariableFont_wdth,wght.ttf`. I tried to reinstall the font with Administrative Installation but the problem is not fixed.



